Autogenerated Questions Paper Draft

### 2018-04-10 paper_draft/paper_draft.tex
Add future work and conclusion

\section{Future Improvements}

- Actual testing (statistics)

- More categories/better questions

- Better distractors

- Also maybe testing of distractor methods? Like how often does a distractor produce a non-unique answer? How often is a distractor actually convincing? This would need a group to review a set of questions.

- Better difficulty classification (also note that this is hard to do ethically)

@@

- A good framework for implementing, generating questions to be easily uploaded online.

>>>>

\section{Future Work}

The next research that should take place is in regards to actual use of the system that produces quantitative results. Any statistics would not only be helpful in evaluating the system as a whole, but also useful in identifying a) the efficacy of each category, b) a statistically-based distinciton between difficulties within categories, and c) efficacy of certain distractor methods for a question. With these results, this system (and other systems) would be better able to produce and classify the questions within them, as well as produce more effective distractor methods. However, there are some ethical problems that will need to be addressed in some of this work. Namely, any test for difficulty between students may cause lower test scores than usual or what is considered "fair", which adversely and unintentionally affects students.

In addition to requiring data, simply adding to the system with more question categories, or improving each question method and each distractor method is always a potential focus.

@@

The proposed system offers instructors a simple interface to easily generate and upload a multitude of multiple choice questions to be used in an online exam. With a unique question used for each student, this will hopefully reduce the presence of cheating in online exams. Along with the many different categories, this system distinguishes between relative difficulty of a question (to challenge and test all students fairly), and it also offers methods of generating convincing distractors to more effectively test student knowledge.
